\documentclass[4paper,25pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{red}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeSubItem}[2]{\item \textbf{#1}: #2}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\LARGE Divas KC} \\[5pt]
    \href{tel:+15512708394}{551-270-8394} \hfill
    \href{mailto:divaskc6@gmail.com}{divaskc6@gmail.com} \hfill
    \href{https://www.linkedin.com/in/divaskc/}{linkedin.com/in/divaskc} \hfill
    \href{https://github.com/dkc01}{github.com/dkc01}
\end{center}

% ---------------- Education ----------------
\section{Education}
\textbf{Ramapo College of New Jersey} \hfill Mahwah, NJ\\
Bachelor of Science in Computer Science \hfill June 2027\\
\textbf{Awards}: Global Scholarship Recipient, College Honors Program, HackRamapo 2026 Winner\\
\textbf{Relevant Coursework}: Machine Learning, Computer Vision, Data Analytics with Python, Data Visualization, Software Design, Data Structures and Algorithms, Operating Systems, Unix Environment, Discrete Structures, Assembly Language

% ---------------- Skills ----------------
\section{Technical Skills}
\begin{itemize}\setlength\itemsep{0em}
    \item \textbf{Languages}: Python, React, C++, SQL
    \item \textbf{ML / AI}: Scikit-learn, Neural Networks (CNNs, RNNs, LSTMs), Embeddings, RAG, Transformers
    \item \textbf{Data \& Visualization}: Pandas, NumPy, Matplotlib, Seaborn, Plotly, Excel
    \item \textbf{Web, Infra \& Tools}: Next.js, React, PostgreSQL, pgvector, Docker, Git, Linux, Jupyter
\end{itemize}

% ---------------- Experience ----------------
\section{Work Experience}

\textbf{Office of Institutional Research} \\
\textit{Data Analyst Intern, Mahwah, NJ \hfill Feb 2024 -- Present}
\begin{itemize}
    \item Supported institutional budgeting and performance reporting by evaluating datasets spanning 1,000+ records.
    \item Increased reporting accuracy by 15\% through systematic data validation, cleaning, and reconciliation.
    \item Developed Excel-based financial models and statistical summaries used in budget planning for 5+ departments.
\end{itemize}

\textbf{Ramapo Information Technology Services} \\
\textit{Student IT Consultant, Mahwah, NJ \hfill Sept 2024 -- Present}
\begin{itemize}
    \item Resolved 20--30 technical support tickets per week involving network connectivity, hardware, and user access for 5,000+ students and staff.
    \item Monitored campus-wide network infrastructure using Cisco Prime, enabling faster identification of performance issues.
    \item Maintained a high-volume ticketing workflow with an average 1-day resolution time and 95\% customer satisfaction.
\end{itemize}

% ---------------- Projects ----------------
\section{Projects}
\resumeSubHeadingListStart

\item \textbf{Personal Canvas – AI-Powered Academic Dashboard (Next.js, TypeScript, PostgreSQL, pgvector, OpenRouter)}
\begin{itemize}
    \item Built a full-stack academic assistant that syncs Canvas LMS data (courses, assignments, grades, announcements) into a local PostgreSQL database via a custom Node.js parser.
    \item Implemented a Retrieval-Augmented Generation (RAG) pipeline using pgvector for vector storage and NVIDIA's LLaMA-Nemotron embedding model to enable semantic search over personal academic data.
    \item Developed an AI chat interface with persistent memory, multi-step tool calling, and automatic conversation compaction to maintain context across sessions.
    \item Delivered streaming AI-generated course insights including assignment prioritization, effort estimation, and grade trend analysis via a Next.js API powered by the Vercel AI SDK.
\end{itemize}

\item \textbf{AskMyDocs – RAG Document Q\&A (Python, FAISS, SentenceTransformers, pdfplumber)}
\begin{itemize}
    \item Designed and implemented a Retrieval-Augmented Generation pipeline to answer questions across 50+ PDF and TXT documents.
    \item Built document ingestion, normalization, and overlapping chunking workflows to index thousands of text segments.
    \item Generated semantic embeddings using SentenceTransformers and executed top-k similarity search with FAISS.
    \item Delivered source-grounded responses with similarity scores, improving answer reliability and reducing hallucinations.
\end{itemize}

\resumeSubHeadingListEnd

% ---------------- Certifications ----------------
\section{Certifications}
Machine Learning (Coursera), Deep Learning (Coursera), CNN (Coursera), Modern React with Redux (Udemy)

\end{document}
